\documentclass{BradyResume}

\address{2206 Dorchester Dr N. \\ Apt 103 \\ Troy, MI 48084}
% TODO default is cornell
\email{brajac709@gmail.com}

\begin{document}
\maketitle
\vspace*{-1em}
\section*{Education}
\subsection*{Cornell University}
\begin{itemize}
\item Masters of Engineering 
\dotfill May 2015
  \begin{itemize}
      \item Mechanical Engineering focus in Dynamics Controls, and Robotics
      \item GPA: 3.92 (4.3 scale)
  \end{itemize}
\item Bachelors of Science 
\dotfill May 2014
  \begin{itemize}
  \item Mechanical Engineering, Minor in Computer Science
  \item GPA: 4.05 (4.3 scale)
  \end{itemize}
\end{itemize}

\section*{Past Employment}
%\datesubsec{Product Development Engineer @ FANUC America Corporation}{2015-Present}
\datesubsec{FANUC America Corporation}{2015-Present}{Product Development Engineer - Applied Motion Group}
\begin{itemize}
  % TODO improve these.
  % Especially position description 
  \item Develop cloud analytics to help predict and prevent robot downtime.
  % Develop, test, and support ZDT motion analytics including dataview development
  \begin{itemize}
    \item Web interface for tracking \& managing robot maintenance tasks using usage data sent from the robot.
    \item Developed an analytic to predict reducer failure based on  robot motion data from production path.
    \item Implemented a high stakes analytic that saved customer millions of dollars from prevented downtime.
  \end{itemize}
  \item Provide technical support to customer service engineers.
  \item Develop robot motion software for Real-time operating system.
  \begin{itemize}
	  \item Tuned motion software for new P-40{\it{i}}A robot, working closely with mechanical engineers to meet life and reliability specifications.
	  \item Developed I/O interface for velocity and position control of axes used for process equipment.
  \end{itemize}
  % Figure out better phrasing for communication w/ Japan
  \item Communicate regularly with Japanese office for product unification and testing.

\end{itemize}
\datesubsec{Cornell University Laboratory for Intelligent Machine Systems}%
           {Summer/Fall 2014}%
           {Research Intern}
\begin{itemize}
  \item Researched hydraulic artificial muscles.
  \item Simulated 7-link bipedal robot gait to extract forces in hydraulic cylinders.
  \item Designed controller for dynomometer test apparatus for artificial muscle bundles and variable recruitment control strategy.
\end{itemize}

\datesubsec{Cornell University Department of Computer Science}%
		   {Spring 2014}%
		   {Teaching Assistant for Computer System %
            Organization and Programming}
\begin{itemize}
  \item Lead discussion sections and held weekly office hours for students.
  \item Helped students to reinforce concepts such as CPU organization, assembly language, low level memory management, and optimization.
\end{itemize}

\datesubsec{Cornell University Fluid Dynamics Research Lab}%
           {Summer 2013}%
           {Research Intern}%
\begin{itemize}
  \item Modelled flow around small-scale vertical-axis wind turbines for different airfoils.
\end{itemize}

\datesubsec{Elite Defensive Tactics}{2009-2010}{Assistant karate instructor}
\begin{itemize}
  \item Taught children (ages 5 and up) self defense.
\end{itemize}


\comment{
\section*{Courses}
\begin{delimlist}{Mechanical}
    \item Mechanical Synthesis (machine shop and design experience) 
    \item Mech. Propertie And Selection of Engr. Materials 
    \item Mechatronics (designed and build small robot) 
    \item Aeronautics (built balsa-wood plane) 
    \item Feedback Control 
    \item Non-Linear Dynamics \& Chaos 
\end{delimlist}

\begin{delimlist}{Computer Science}
    \item Machine Learning 
    \item Computer System Organization and Programming 
    \item Function Programming 
    \item Autonomouse Mobile Robots 
    \item Heuristics for Optimization 
    \item Computer Vision 
    \item Robotic Manipulation
\end{delimlist}
}

\section*{Computer Skills}
\begin{delimlist}{Programming}
    \item Java
    \item Python
    \item MATLAB
    \item C
    \item MIPS
    \item OCaml
    \item HTML
    \item PHP
    \item MySQL
    \item Javascript
    \item JQuery
    \item Simulink 
    \item LabView
    \item ROS
    \item UNIX
    \item AngularJS
    \item jqPlot
    \item C\#
    \item .NET
    \item Apache Hadoop
\end{delimlist}

\begin{delimlist}{CAD/Simulation}
    \item SolidWorks
    \item ANSYS
\end{delimlist}

\begin{delimlist}{Other}
    \item \LaTeX\ 
    \item Microsoft Office%
    \item Excel
    \item Google Docs
    \item Git
    \item Clearcase
\end{delimlist}

\section*{Other Experiences}
Section Leader and Rank Leader in Big Red Marching Band \dotfill Spring 2012\\
3D graphics modeling and animating using Blender 3D

\end{document}
